\hypertarget{course5}{}\chapter*{COURSE 5: Maintaining Employment - Advancing Your Career}\label{course5}\addcontentsline{toc}{chapter}{COURSE 5: Maintaining Employment Advancing Your Career}
\extramarks{ }{COURSE 5: Maintaining Employment - Advancing Your Career}
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\localtableofcontents
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}
\newpage
\pagebreak \section*{Module 1:	Ideas, Tips, and Resources for Success in Your New Job}\addcontentsline{toc}{section}{Module 1:	Ideas, Tips, and Resources for Success in Your New Job}\extramarks{Module 1}{COURSE 5: Maintaining Employment - Advancing Your Career}
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}
\etocsetnexttocdepth{4}
\localtableofcontents
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}
\leftskip=0.5cm

The journey is not over yet! Once you've been hired, it's important to stay in your position. Often, new employees do not identify and use the tools necessary to remain employed. These tools are just as important to your success as the ones you've used to find and land that great job.

Here are some ideas, tips, and resources that will help you stay on the right track to success in your new job.
\pagebreak \subsection*{1-1\quad Do Some Research}
\addcontentsline{toc}{subsection}{1-1\quad Do Some Research}
Read through the articles on the APH CareerConnect and NSITE Connect websites to continually sharpen your skills. You can also read through relevant articles on LinkedIn for the latest in industry news and trends.

\pagebreak \subsection*{1-2\quad Succeed at Your Job}
\addcontentsline{toc}{subsection}{1-2\quad Succeed at Your Job}

\href{https://aphcareerconnect.org/succeed-at-work/succeeding-at-your-job/solving-problems-at-work/}{Building Positive Work Habits}

The Perfect Worker: A discussion of work habits that help employees succeed on the job. You will learn what work habits are common in most successfully employed individuals. These habits are developed and practiced through experience. If you practice these in your everyday life, it will be easier to use them in a work setting.

\href{https://aphcareerconnect.org/succeed-at-work/succeeding-at-your-job/solving-problems-at-work/}{Preparing for Your First Month at Work}

This article addresses the expectations that employers have for new employees during the first year on the job. As a new employee, it's important to demonstrate your value and competence on the job to your supervisor and coworkers.

\href{https://aphcareerconnect.org/succeed-at-work/succeeding-at-your-job/solving-problems-at-work/}{The Key to Improving Relationships on the Job}

Most conflict in the workplace is due to communication problems. This article explains the ``Dos'' and ``Don'ts'' of communication on the job and provides tips that you can follow both in your workplace and in your everyday life.

\href{https://aphcareerconnect.org/succeed-at-work/succeeding-at-your-job/solving-problems-at-work/}{Solving Problems at Work}

We all encounter problems on the job. This article explores some common on- the- job-problems and the strategies you can use to solve them.

\subsubsection*{Quick Tips}
\subsubsection*{Talk about it}. Contact your mentors to discuss what makes a successful worker. Ask successfully employed members of your personal network what the secrets are to maintaining a job.

\subsubsection*{Establish and manage expectations proactively}. Unrealistic expectations can be an issue for any new employee, whether it's your unrealistic expectations of what a job will be or an employer's unrealistic expectations of you and your performance. Part of successful employment is managing others' expectations.

As you no doubt have found in the job descriptions you've encountered during this course, employers expect many job duties to be completed by each employee. In a tighter economy, job duties multiply even more and it can be difficult to keep things on track and productive. Manage your time and effort by completing the most important tasks first. Because each manager is different, you'll need to make an effort to find out what your supervisor values and what he or she specifically expects from you.

\subsubsection*{Perform all job duties to your best abilities}. No task is too small or menial.

\subsubsection*{Complete your duties and tasks on time}. This should seem obvious, but missing deadlines is a quick way to lose your job. The saying ``time is money'' is no lie. Many people lack crucial time management skills.

Something as simple as consistently using a personal calendar can be the difference between a paycheck and an unemployment check.

\subsubsection*{Dress appropriately}. Make sure to monitor the clothing that you wear to work. Clothing wears out, develops stains and discoloration, stretches out or shrinks over many washes. It's important make sure that your wardrobe is maintained to meet appropriate standards for the workplace.

\subsubsection*{Practice your skills}. The skills you have learned in this course are not just job seeking skills, they are professional skills for success. Regularly review and practice these skills.

\subsubsection*{Maintain a professional demeanor}. Don't become too familiar with your coworkers or boss. Workplaces can be friendly, but you must remember that your primary relationships and responsibilities at work will always be professional ones. Your behavior should reflect that understanding at all times.

\subsubsection*{Be Discreet}. Personal information you share may haunt you in the future. Often your coworkers become friends, but it's important to keep information that could be damaging to your image or career to yourself.

\subsubsection*{Regularly review your job description}. Most organizations have mandatory work or performance evaluations. Typically, these evaluations monitor your level of performance on the job in the areas and tasks defined in your job description. Regularly review your job description to make sure you're fulfilling your duties, and make sure that you're working on addressing any areas you know are weaknesses.

\subsubsection*{Practice common courtesy}. Proper social interactions with coworkers and consumers is a MUST on the job. All workplaces require that social norms (typical expected behaviors) be maintained at some level. These social norms may not be the same at every business, but it's best to be safe by being courteous, appropriately social, and professional at all times. Remembering to say ``hello,'' ``goodbye,'' ``good morning,'' ``have a good night,'' ``please,'' and ``thank you'' are small actions that help a workplace feel friendly and establish good relations with your colleagues.

\subsubsection*{Your first job is just the beginning of your professional life}. Once you are employed, we encourage you to volunteer as a mentor for someone else so you can share your experience and advice with others.


\pagebreak \section*{Module 2: Professional Development and Continuous Career Planning}\addcontentsline{toc}{section}{Module 2: Professional Development and Continuous Career Planning}\extramarks{Module 2}{COURSE 5: Maintaining Employment - Advancing Your Career}
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}} \etocsetnexttocdepth{4} \localtableofcontents
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}

\pagebreak \subsection*{2-1\quad Identify Appropriate Professional Development Opportunities}
\addcontentsline{toc}{subsection}{2-1\quad Identify Appropriate Professional Development Opportunities}

Take initiative of your professional development to ensure you are able to continuously hone your skills and set yourself up for success in the current position and for potential future career advancement.

Your new employer may offer \textbf{internal professional development} (opportunities within your workplace) that are required and/or optional. Make sure you discuss what training you should complete and build a professional development calendar for yourself. Make your professional development an integral part of regular performance conversations with your supervisor.

You can also pursue \textbf{external professional development} opportunities. Seek occasions and undertakings which will help you remain relevant in your career field and equip you for leadership opportunities. Acquire up-to-date research and skills by attending relevant conferences, workshops, or webinars; complete related coursework; subscribe to pertinent newsletters, magazines, publications, and journals; network with professionals in your field to idea-share; and seek mentorship from individuals who have skills-sets which you can learn. Consider, too, teaching a course or presenting at a conference—you will be highly motivated to remain current in your field.

Lastly, you will likely be tasked with a work responsibility that will stretch you, or your manager will likely ask your team for a volunteer to tackle a substantial task; consider accepting the opportunity if you’re willing to learn and be committed to success. You’ll develop skills and your supervisor will learn you’re flexible, hard-working, and you rise to the occasion.
\pagebreak \subsection*{2-2\quad Maintain Focus on Your Career Path}
\addcontentsline{toc}{subsection}{2-2\quad Maintain Focus on Your Career Path}

Consider your career goals. Would you like to develop leadership skills? Increase your job responsibilities? Acquire a new work-related skill? Network? After ensuring you are providing accurate and quality work and are spending your time on tasks you’re expected to accomplish, consider how you can assume additional responsibilities or pursue professional development which will enable you to progress on your career path.


\pagebreak \section*{Module 3:	Resources and Professional Development Opportunities}\addcontentsline{toc}{section}{Module 3:	Resources and Professional Development Opportunities }\extramarks{Module 3}{COURSE 5: Maintaining Employment - Advancing Your Career}
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}
\etocsetnexttocdepth{4} \localtableofcontents
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}

\pagebreak \subsection*{3-1\quad Digital Resources}
\addcontentsline{toc}{subsection}{3-1\quad Digital Resources}

You may find the following resources and associations valuable as you journey along your career path. Peruse the list, which will be periodically updated, and utilize the resources which will assist you in reaching your career goals. The list is designed for the sole purpose of providing recommended resources, not as part of a mandatory activity.

\begin{table}[h!]
	\centering
	\begin{tabular}{ll}
		APH CareerConnect:\dotfill                            & \href{https://aphcareerconnect.org/}{https://aphcareerconnect.org/}         \\
		NSITE:\dotfill                                        & \href{www.nsite.org}{www.nsite.org}                                         \\
		NSITE Connect:\dotfill                                & \href{https://nsiteconnect.jobboard.io/}{https://nsiteconnect.jobboard.io/} \\
		NSITE Professional Development Opportunities:\dotfill & \href{https://nsite.org/training/}{https://nsite.org/training/}             \\
		NSITE LinkedIn:\dotfill                               & \textbf{Follow APH, NSITE, NIB, etc}                                        \\
	\end{tabular}
\end{table}

\begin{itemize}[leftmargin=1.0cm]
	\item Consumer Groups and Professional Associations:
	      \begin{itemize}
		      \item \href{https://www.acb.org/blind-low-vision-resources}{American Council of the Blind (acb.org)/ Blind/Low Vision Resources | American Council of the Blind (acb.org)}
		      \item \href{https://nfb.org/resources}{National Federation of the Blind (nfb.org)/ Resources | National Federation of the Blind (nfb.org)}
		      \item \href{https://www.afb.org/}{American Foundation for the Blind (afb.org)}
		      \item \href{https://aphconnectcenter.org/}{The American Printing House for the Blind/APH ConnectCenter (aphconnectcenter.org)}
		      \item \href{https://www.nib.org/resources/#skip_link_main_content}{Welcome to NIB | Careers for the Blind/ Career Resources | National Industries for the Blind (nib.org)}
		      \item \href{https://www.wsblind.org/resources}{World Services for the Blind (wsblind.org)/ Resources — World Services for the Blind (wsblind.org)}
		      \item \href{https://www.abilityone.gov/}{AbilityOne}
		      \item Consider career-specific consumer groups and professional associations.
	      \end{itemize}
	\item Professional Publications:
	      \begin{itemize}
		      \item \href{https://www.afb.org/news-publications/publications/jvib}{JVIB | American Foundation for the Blind (afb.org)}
		      \item Consider career-specific professional publications.
	      \end{itemize}
	\item Continuing Education and Support Resources:
	      \begin{itemize}
		      \item \href{https://nam11.safelinks.protection.outlook.com/?url=https%3A%2F%2Frsa.ed.gov%2Fabout%2Fstates&data=05%7C01%7Cchris_fendrick%40kernhigh.org%7Cbc7ebcd1034f4b8956c808da4e0886ed%7C79e9a47a04484925bf6638dadfc6f0a4%7C0%7C0%7C637908095803823825%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=7Yp0WqYpmUt23krj04UuAfM%2FfPtXDqngbOewfl9go10%3D&reserved=0}{Rehabilitation Services Administration (RSA) (ed.gov)}
		      \item \href{https://nam11.safelinks.protection.outlook.com/?url=https%3A%2F%2Frsa.ed.gov%2Fabout%2Fstates&data=05%7C01%7Cchris_fendrick%40kernhigh.org%7Cbc7ebcd1034f4b8956c808da4e0886ed%7C79e9a47a04484925bf6638dadfc6f0a4%7C0%7C0%7C637908095803823825%7CUnknown%7CTWFpbGZsb3d8eyJWIjoiMC4wLjAwMDAiLCJQIjoiV2luMzIiLCJBTiI6Ik1haWwiLCJXVCI6Mn0%3D%7C3000%7C%7C%7C&sdata=7Yp0WqYpmUt23krj04UuAfM%2FfPtXDqngbOewfl9go10%3D&reserved=0}{State Vocational Rehabilitation Agencies}
		      \item \href{https://aphconnectcenter.org/TransitionHub/}{APH ConnectCenter Transition Hub (aphconnectcenter.org)}
		      \item \href{https://www.dol.gov/agencies/eta/wioa#main-content}{Workforce Innovation and Opportunity Act | U.S. Department of Labor (dol.gov)}
		      \item \href{https://www.dol.gov/general/topic/training/onestop#main-content}{American Job Centers | U.S. Department of Labor (dol.gov)}
		      \item \href{https://www.resumebuilder.com/comprehensive-resume-and-career-guide-for-people-with-disabilities/}{Resume and Employment Guide for People with Disabilities - ResumeBuilder.com}
		      \item \href{https://www.ntac.blind.msstate.edu/consumers/webinars-podcasts}{Welcome to Our Webinars and Podcasts: Employment Insights with the NRTC | National Technical Assistance Center (msstate.edu)}
		      \item \href{https://www.ntac.blind.msstate.edu/consumers}{For People who are Blind or have Low Vision | National Technical Assistance Center (msstate.edu)}
		      \item \href{https://askjan.org/}{JAN - Job Accommodation Network (askjan.org)}
		      \item \href{https://www.khanacademy.org/search?referer=%2F&page_search_query=careers}{Careers | Khan Academy}
		      \item \href{https://www.khanacademy.org/college-careers-more/career-content/manage-people-and-processes#main-content}{Manage People and Processes | Careers | Life skills | Khan Academy}
		      \item \href{https://hadley.edu/}{Hadley Vision Resources | 100 Years of Empowering Adults with Vision Loss}
		      \item \href{https://hadley.edu/learn#main-content?topic_id=16}{Working Skills-Hadley Vision Resources | Free Resources For Living with Low Vision}
		      \item Consider career-specific continuing education opportunities and resources.
	      \end{itemize}
	\item Financial Resources:
	      \begin{itemize}
		      \item \href{https://www.ssa.gov/work/}{The Work Site (ssa.gov)}
		      \item \href{https://www.ssa.gov/redbook/}{Using Your PASS - Ticket to Work - Social Security (ssa.gov)}
		      \item \href{https://www.ssa.gov/redbook/}{Social Security Online - The Red Book - A Guide to Work Incentives (ssa.gov)}
		      \item \href{https://www.irs.gov/government-entities/federal-state-local-governments/able-accounts-tax-benefit-for-people-with-disabilities}{Financial Education and Incentives | U.S. Department of Labor (dol.gov)}
		      \item \href{https://www.irs.gov/government-entities/federal-state-local-governments/able-accounts-tax-benefit-for-people-with-disabilities}{ABLE Accounts - Tax Benefit for People with Disabilities | Internal Revenue Service (irs.gov)}
		      \item \href{https://www.investopedia.com/guide-to-financial-literacy-4800530}{The Ultimate Guide to Financial Literacy (investopedia.com)}
	      \end{itemize}
	\item Assistive Technology Resources:
	      \begin{itemize}
		      \item \href{https://aira.io/#content}{Visual Interpreting – Get Live, On-demand Access to Visual Information (aira.io)}
		      \item \href{https://support.apple.com/en-us/HT209585}{How to Contact Apple for Accessibility Support}
		      \item \href{https://www.applevis.com/}{AppleVis}
		      \item \href{https://www.bemyeyes.com/}{Be My Eyes - See the world together}
		      \item \href{https://www.microsoft.com/en-us/Accessibility/disability-answer-desk?activetab=contact-pivot%3aprimaryr9}{Computers for the Blind}
		      \item \href{https://www.microsoft.com/en-us/Accessibility/disability-answer-desk?activetab=contact-pivot%3aprimaryr9}{Disability Answer Desk Support | Microsoft Accessibility}
		      \item \href{https://www.freedomscientific.com/training/fusion/}{Fusion training from Freedom Scientific}
		      \item \href{https://hims-support.com/}{HIMS Support | (hims-support.com)}
		      \item \href{https://support.humanware.com/en-usa/support}{Humanware - Home - Low Vision \& Blindness Solutions}
		      \item \href{http://www.ibugtoday.com/}{iBlind Users Group}
		      \item \href{https://www.nvaccess.org/}{NV Access: Empowering lives through non-visual access to technology}
		      \item \href{https://viewplus.com/#main}{ViewPlus Technologies - Braille Embossers \& Tactile Graphics}
		      \item \href{https://www.freedomscientific.com/training/zoomtext/}{ZoomText Training from Freedom Scientific}
		      \item \href{https://www.maxiaids.com/}{MaxiAids | Independent Living, Low Vision, Blind, Mobility}
	      \end{itemize}
	\item Dog Guide Resources:
	      \begin{itemize}
		      \item \href{https://www.guidedogs.com/}{Guide Dogs for the Blind}
		      \item \href{https://www.seeingeye.org/}{The Seeing Eye}
		      \item \href{https://www.leaderdog.org/}{Leader Dogs for the Blind}
		      \item \href{https://www.guidedogsofamerica.org/}{Guide Dogs of America}
		      \item \href{https://guidedogsofthedesert.org/}{Guide Dogs of the Desert | California}
		      \item \href{https://www.guidedogs.org/#content}{Southeastern Guide Dogs}
		      \item \href{https://www.guidingeyes.org/}{Guiding Eyes for the Blind - Guide Dogs for People with Vision Loss}
		      \item \href{http://www.freedomguidedogs.com/}{Freedom Guide Dogs for the Blind}
		      \item \href{https://fidelco.org/}{Pilot Dogs}
		      \item \href{https://fidelco.org/}{Fidelco Guide Dog Foundation}
		      \item \href{https://guidedogsoftexas.org/}{Guide Dogs of Texas}
		      \item \href{https://occupaws.org/}{OccuPaws}
	      \end{itemize}
	\item Mainstream Career Resources:
	      \begin{itemize}
		      \item \href{https://www.linkedin.com/check/add-phone?country_code=us}{LinkedIn}
		      \item \href{https://www.ziprecruiter.com/search-jobs?tsid=101050007&utm_source=dgljs|bing-search|cmp-396131150|adg-1254543268869339|kw-kwd-78409208661568:loc-190|mt-e|device-c|cr-78409109849992|uid-08a564f52ea21ef2af2d06534b6fc1dc&utm_medium=cpc&msclkid=08a564f52ea21ef2af2d06534b6fc1dc}{Job Search - Millions of Jobs Hiring Near You | ZipRecruiter}
		      \item \href{https://www.wsj.com/}{The Wall Street Journal - Breaking News, Business, Financial \& Economic News, World News and Video (wsj.com)}
		      \item \href{https://www.forbes.com/?sh=36ffc04c2254}{Forbes}
	      \end{itemize}\end{itemize}
\pagebreak \subsection*{3-2\quad Additional Resources: Articles/ Videos}
\addcontentsline{toc}{subsection}{3-2\quad Additional Resources: Articles/ Videos}
\begin{itemize}[leftmargin=1.0cm]
	\item \href{https://aphcareerconnect.org/succeed-at-work/our-stories/}{Personal Employment Stories: People Who Are Blind or Low Share Their Employmnet Stories (APH CareerConnect)}
	\item \href{https://www.wsblind.org/blog/2020/8/20/public-transportation-tips-for-the-blind-and-visually-impaired}{Public Transit Tips for the Visually Impaired and Blind — World Services for the Blind (wsblind.org)}
	\item Department of Labor Video Series: \href{https://www.dol.gov/agencies/odep/program-areas/individuals/youth/transition/soft-skills/videos}{Videos | U.S. Department of Labor (dol.gov) }
	      Here is a sample of the U.S. Department of Labor Videos
	      \begin{itemize}
		      \item \href{https://www.youtube.com/watch?v=X0voPlW2pSs}{Communication Skills}
		      \item \href{https://www.youtube.com/watch?v=7dPWVjQSad4}{Professionalism }
		      \item \href{https://www.youtube.com/watch?v=OyLlS_XF9to}{Apprenticeships}
	      \end{itemize}\end{itemize}