\hypertarget{intro}{}\chapter*{Introduction}\label{intro}
\renewcommand{\cftchapleader}{\cftdotfill{\cftdotsep}}

\pagestyle{fancyplain}
\fancyfoot[C]{\thepage}
\noindent\makebox[\textwidth]{\rule{\linewidth}{0.4pt}}
The purpose of The Jobseeker's Toolkit is to help you acquire and build critical tools that will ultimately help you conduct a successful job search. Through a series of five courses with a focus on four key components, you will build your own toolkit that helps prepare you for the challenges of a job search.

The five courses are structured into modules and activities that build on the content and exercises of the preceding course. It is therefore imperative that you work your way through the series in chronological order and complete every assignment along the way. Once you feel that you possess the skills covered in each section, you will have an opportunity to apply what you have learned by completing the section “From Theory to Practice.”

Throughout the series, you will find a number of lessons and assignments that will help you develop and hone your job seeking skills. In other words, the work you put into building your own Toolkit will provide you with a foundation for success.

The Jobseeker’s Toolkit Course Series is built to accompany you through the job search and employment lifecycle, from building self-awareness to determining the best-fit career path, identifying employment opportunities, preparing for an interview, all the way to maintaining employment and advancing your career.

Courses 1 and 2 will help you discover your career interests:

\textbf{Course 1: Self-Awareness} covers self-assessment and evaluation.

\textbf{Course 2: Career Exploration – Methods and Resources} is all about helping you explore the career options that may be right for you.

Courses 3 and 4 will help you find job opportunities and hone the skills that will help you get a job offer.

\textbf{Course 3: Finding Employment} dives into the tools necessary for finding job opportunities.

\textbf{Course 4: The Interview} is about sharpening your interview skills and landing a desired position.

The final course in the series of The Jobseeker’s Toolkit provides information on job maintenance and what it takes to be a successful employee. It will also point you to further resources that will help with continued professional development on your chosen career path.

\textbf{Course 5: Maintaining Employment – Advancing Your Career} will help you prepare for success once you have secured the position and will help you advance on your career path.

The Jobseeker's Toolkit was modeled after the American Printing House for the Blind Transition Tote, which was created by Dr. Karen Wolffe. Dr. Wolffe provided consultation on this project. We are grateful to all contributing parties and reviewers who helped create this resource.

\clearpage
\mbox{}
